Psychophysics of musical elements in the discrete-time representation of sound

### 2017-07-02 article/acm/body.tex
melhoradas figuras do artigo

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/delays_}
    \caption{Convolution with the impulse: shifting (a), delay lines (b) and granular synthesis~(c). Represented in increasing order of its pulse density.}
        \label{fig:delays}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/iir_}
    \caption{Modules for the frequency response (a), (b), (c) and (d) for IIR filters of equations~\ref{eq:passa-baixas}, \ref{eq:passa-altas}, \ref{eq:passa-banda} and \ref{eq:rejeita-banda} respectively, considering different cutoff frequencies, center frequencies and band width.}
        \label{fig:iir}
\end{figure*}

@@

\begin{figure*}
	\hspace*{-.75cm}
         \includegraphics[width=1.1\textwidth]{figures/ruidos}
     \caption{Colors of noise generated by equations~\ref{eq:branco}, \ref{eq:rosa}, \ref{eq:marrom}, \ref{eq:azul} and \ref{eq:violeta}: spectrum and waveforms.}
         \label{fig:ruidos}
\end{figure*}

@@

\begin{figure}[h!]
     \centering
         \includegraphics[width=\columnwidth]{figures/vibrato}
     \caption{Spectrogram of a sound with a sinusoidal vibrato of $3Hz$ and one octave of depth in a $1000Hz$ sawtooth wave, with $f_s=44.1kHz$.}
         \label{fig:vibrato}
\end{figure}

@@

\begin{figure*}
     \centering
         \includegraphics[width=\textwidth]{figures/tremolo}
     \caption{Tremolo with a depth of $V_{dB}=12dB$, with a sawtooth waveform as its oscillatory pattern, with $f'=1.5Hz$ in a sine of $f=40Hz$ (sample frequency $f_s=44.1kHz$).}
         \label{fig:tremolo}
\end{figure*}

@@

\begin{figure}[htp!]
    \centering
        \includegraphics[width=\columnwidth]{figures/adsr}
    \caption{An ADSR envelope (\emph{Attack, Decay, Sustain, Release}) applied to an arbitrary sound sequence. The linear variation of the amplitude is above, in blue. Below the amplitude variation is exponential.}
        \label{fig:adsr}
\end{figure}

>>>>

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/delays_}
    \caption{Convolution with the impulse: shifting (a), delay lines (b) and granular synthesis~(c). Represented in increasing order of its pulse density. The vertical axis is related to amplitude although one should keep in mind that each plot has two or three displaced signals.}
        \label{fig:delays}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/iir__}
    \caption{Modules for the frequency response (a), (b), (c) and (d) for IIR filters of equations~\ref{eq:passa-baixas}, \ref{eq:passa-altas}, \ref{eq:passa-banda} and \ref{eq:rejeita-banda} respectively, considering different cutoff frequencies, center frequencies and band width.}
        \label{fig:iir}
\end{figure*}

@@

\begin{figure*}
	\hspace*{-.75cm}
         \includegraphics[width=1.\textwidth]{figures/ruidos_}
     \caption{Colors of noise generated by equations~\ref{eq:branco}, \ref{eq:rosa}, \ref{eq:marrom}, \ref{eq:azul} and \ref{eq:violeta}: spectrum and example waveforms.}
         \label{fig:ruidos}
\end{figure*}

@@

\begin{figure}[h!]
     \centering
         \includegraphics[width=\columnwidth]{figures/vibrato_}
     \caption{Spectrogram of a sound with a sinusoidal vibrato of $3Hz$ and one octave of depth in a $1000Hz$ sawtooth wave, with $f_s=44.1kHz$.}
         \label{fig:vibrato}
\end{figure}

@@

\begin{figure*}
     \centering
         \includegraphics[width=\textwidth]{figures/tremolo_}
     \caption{Tremolo with a depth of $V_{dB}=12dB$, with a sawtooth waveform as its oscillatory pattern, with $f'=1.5Hz$ in a sine of $f=40Hz$ (sample frequency $f_s=44.1kHz$).}
         \label{fig:tremolo}
\end{figure*}

@@

\begin{figure}[htp!]
    \centering
        \includegraphics[width=\columnwidth]{figures/adsr_}
    \caption{An ADSR envelope (\emph{Attack, Decay, Sustain, Release}) applied to an arbitrary sound sequence. The linear variation of the amplitude is above, in blue. Below the amplitude variation is exponential.}
        \label{fig:adsr}
\end{figure}
